Decorrelating Errors in Quantum Gates by Random Gate Synthesis

### 2018-03-17 decorrelation.tex
added images, added some comments to the tex file, added a readme in the image folder

\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm, algorithmicx}
\usepackage{algpseudocode}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=}
%\hypersetup{citecolor={blue}, colorlinks={true}, filecolor={blue},
%   linkcolor={blue}, pdfauthor=, pdfkeywords= pdfsubject=, pdftitle=,
%   urlcolor{blue}}

\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}

@@

\begin{algorithmic}
\Procedure{find\_controls}{U, $\delta$, $u_{ij}$}
\While{$J(U) < (1-\delta$)}
\State $u_{ij}$ $\rightarrow$ $u_{ij} + \epsilon\frac{\partial J(U)}{\partial u_{ij}}$
\State $U \rightarrow \exp\{-it(H_0 + \sum_{i=0}^{n}(c_i(t)H_i)\}$
\EndWhile
\EndProcedure
\end{algorithmic}

In general these gradients can be computed via simple back propagation with the chain rule, however in \cite{Khaneja2005} Khaneja et al. derives a simple update formula that is correct to first order. So long as the discretization in time is fine enough,this will be a good approximation.

@@

$$ H = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y) $$

\section{2Q Gate}
We assume a model of our Hamiltonian for two qubit control to be:
$$H = \sum_{j=1}^2\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)$$

\begin{align*}
    \left( U^\dagger V \right)
\end{align*}

>>>>

\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode, caption}
\hypersetup{colorlinks=true, pdfauthor=Kevin C. Young, pdftitle=}
%\hypersetup{citecolor={blue}, colorlinks={true}, filecolor={blue},
%   linkcolor={blue}, pdfauthor=, pdfkeywords= pdfsubject=, pdftitle=,
%   urlcolor{blue}}

\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}

@@

\begin{algorithm}[H]
\floatname{algorithm}{Procedure}
  \caption*{\textsc{\textbf{Gradient Ascent}}}
   \begin{algorithmic}
\While{$J(U) < (1-\delta$)}
\State $u_{ij}$ $\rightarrow$ $u_{ij} + \epsilon\frac{\partial J(U)}{\partial u_{ij}}$
\State $U \rightarrow \exp\{-it(H_0 + \sum_{i=0}^{n}(c_i(t)H_i)\}$
\EndWhile

   \end{algorithmic}
\end{algorithm}

In general these gradients can be computed by propagating partial derivatives of the cost function with respect to control parameters via the chain rule. However, in \cite{Khaneja2005} Khaneja et al. derive a simple update formula that is correct to first order, in particular one can show that:
\begin{align}
\frac{\partial J(U)}{\partial u_{ij}} = -2Re\{\braket{{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}}{i\Delta tH_jU_j...U_1}\\
\braket{U_j...U_1}{U_{j+1}^{\dagger}...U_N^{\dagger} U_T}\} +  \mathcal{O}(\Delta t^2)
\end{align}

In this paper we have modified the update step to use instead use approximately the following gradient:
\begin{align}
\int p(\vec{\delta})\frac{\partial J(U(\vec{\delta})}{\partial u_{ij}} d\vec{\delta}
\end{align}
again with $p(\vec{\delta})$ Gaussian. In particular, this ensures that the optimizer will attempt to find controls that are not only good at zero detuning, but also for small noise values.
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{x2.png}
\caption{In the above we have used our method to produce a BCS for a $RX(\frac{\pi}{2})$ pulse, with the Hamiltonian given in \ref{eq:1Qham}. A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$. B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
\end{figure*}
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{y2.png}
\caption{In the above we have used our method to produce a BCS for a $RY(\frac{\pi}{2})$ pulse, with the Hamiltonian given in \ref{eq:1Qham}. A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$. B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
\end{figure*}

@@

\begin{equation}\label{eq:1Qham}
H = \epsilon\sigma_z + (1 + \delta)(c_x(t)\sigma_x + c_y(t)\sigma_y)
\end{equation}
We assume variances of $\sigma = .001$ on all control parameters, and we use a control time of $\pi$, with 100 steps of discretization. We assume that the errors on $\sigma_x$ and $\sigma_y$ are perfecly correlated.
%These plots take a little while to make, so I can't iterate *that* fast - clearly the fonts need to be bigger, and there should be a title what else add a legend saying the black is the optimal?
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{2Q.png}
\caption{In the above we have used our method to produce a BCS for a ZZ($\frac{\pi}{2}$) entangling gate with controls given by \ref{eq:2Qham}. A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$. B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
\end{figure*}

\section{2Q Gate}
We assume a model of our Hamiltonian for two qubit control to be:
\begin{equation} \label{eq:2Qham}
H = \sum_{j=1}^2\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)
\end{equation}
We assume that the standard deviations are $\sigma = .001$ on all parameters, and that the control time is 4 $\pi$, with discretization of 500 steps. In addition, we assume that errors on the single qubit $\sigma_x$ and $\sigma_y$ rotations are correlated. Namely, because in many systems like superconducting qubits, the difference between these pulses amounts to a phase shift in the signal, so that things like amplitude drift will be shared and correlated.
%It might be interesting to show a dhistogram of the pribabilities assigned to each control to show that they aren't all zero. and maybe
